%!TEX root = ../dissertation.tex
% the abstract

OpenCog is an open source software framework oriented towards Artificial General Intelligence (AGI).  It consists of a diverse assemblage of cognitive algorithms, each embodying its own innovations and having a powerful overall architecture due to its careful adherence to the principle of Cognitive Synergy, which is a principle suggesting a possible general intelligence architecture based on different interconnected knowledge creation mechanisms. \\
This project deals with a category of Task Planning problems, which involve a robot manipulator interacting with objects, using some of the OpenCog modules. 
These OpenCog modules are used as the backbone of the knowledge base and make possible both the description of domain and problem features, and the interaction with them.
The aim is to obtain a system capable of solving any manipulation problem that has a domain with the specific actions: Pick, Place, Stack and Unstack. \\ 
At the beginning, artificial intelligence (AI) is briefly presented, focusing in particular on AGI and its role in this project. Afterwards, the main components of the OpenCog system and some of its modules are described. This is followed by a general formulation of the problem starting from the well-known-in-AI blocks world problem, to arrive at the practical implementation of the system. It describes how the system is designed and how the modules of OpenCog are used. Furthermore, it contains a search algorithm specifically developed to solve manipulation problems by exploiting some of these OpenCog modules. In conclusion, an assembly test of an industrial component is provided and solved, and the results are analysed. \\